Fitting phylogenetic generalized linear mixed-effect models using lme4

### 2017-10-17 ms.tex
need to clean up repo before moving forward
all cases are done, single case is not that stable

Something about phylogenetic applications. This growing field has produced a number of statistical tools and software corde to implement them ... but this code is disparate and handles data differently, making routine data analyese challenging. ...

Here we present 
\section{Methods}

>>>>

Given a phylogenetic tree, phylogenetic models aim to find parsimonious methods that can be used to link ecological phenomena with the evolutionary processes that generate species and their traits. 
Ecologist have long considered the effects of functional traits and environmental conditions on pheotypic traits. 
For example, regression analyses of body temperature as a function of body size for animal within a clade, species compositions in different sites, etc.

\section{Methods}

The standard problem of phylogenetic comparative methods is to analyze relationships among data where the observations are gathered from nodes (usually tips) of a phylogenetic tree.

An alternative approach is to model the phylogenetic correlation as a gaussian process. In particular, suppose that the evolutionary process is a Brownian motion. In that case, the phylogenetic variability of a particular observation can be written as the sum of the evolutionary changes that occurred on all of the branches in the phylogeny in its past. If we set up the Z matrix appropriately, we can model everythign with a sequence of independent errors, rather than having to do a fancy things to impose a correlation structure on the random effects.
